A modelling strategy to improve cacao quality and productivity

### 2021-10-07 papers/model/paper_model.tex
results in progress

%  %  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

@@

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, analytica, animals, antibiotics, antibodies, antioxidants, appliedchem, applmech, applmicrobiol, applnano, applsci, arts, asi, atmosphere, atoms, audiolres, automation, axioms, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomechanics, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, brainsci, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coatings, colloids, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, crops, cryptography, crystals, curroncol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entropy, environments, environsciproc, epidemiologia, epigenomes, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forensicsci, forests, fractalfract, fuels, futureinternet, futuretransp, futurepharmacol, futurephys, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, land, languages, laws, life, liquids, literature, livers, logistics, lubricants, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, metabolites, metals, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, minerals, mining, modelling, molbank, molecules, mps, mti, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photochem, photonics, physchem, physics, physiolsci, plants, plasma, pollutants, polymers, polysaccharides, proceedings, processes, prosthesis, proteomes, psych, psychiatryint, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, smartcities, sna, societies, socsci, soilsystems, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, systems, taxonomy, technologies, telecom, textiles, thermo, tourismhosp, toxics, toxins, transplantology, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wevj, women, world

@@

% Authors, for the paper (add full first names)
\Author{Angela RV $^{1,\dagger,\ddagger}$\orcidA{}, Adriana $^{1,\ddagger}$ and Anyela VCR$^{1,}$*}

@@

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Lastname, F.; Lastname, F.; Lastname, F.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Crop modelling can support agronomical decisions of crop production under a range of scenarios improving competitiveness. Cocoa production systems in Latin America has a high importance over social and economic development, facing  the fight against hunger and poverty. Cocoa fruits development can be considered as the result of a number of physiological and morphological processes that can be described by mathematical relationships even under uncontrolled environments. We parametrized the SIMPLE crop model \citep{Zao2019simple} to predict the best time for harvest cocoa fruits in Colombia. The aim of this study is develop a practical tool for farmers using flowering date and weather variables (Solar radiation, rain and temperature) easily available for crop modelling to understand and predict the phenology of cacao trees which is key to produce high quality cacao beans. }

@@

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{Instead of the abstract}
%\entrylink{The Link to this entry published on the encyclopedia platform.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setcounter{section}{-1} %% Remove this when starting to work on the template.

@@

Cocoa is a cauliflorous plant, which means that flowers grow on the trunk and branches. In Colombia cocoa trees usually produce flowers throughout the year, however the biggest flowering occurs in September and January to harvest in March and July (Fig.\ref{fig:yield}). Cocoa trees produces with up to 10000 flowers per tree each year. which the 50 \%  do not develop into ripe fruits according to Fedecacao reports. The flower takes 30 days passing by 12 micro-stages from meristem development (stages 1–6) to the fully developed flower(Stages 7–12) \citep{swanson2005} when it is ready to be pollinated. 2005). The opening of flowers or anthesis  occurs over a 12-hour period during the night and it is synchronised between the groups of mature flowers \citep{Niemenak2010}. However, the live of a flower can last approximately 1 day after the opening falling form the trunk if it is unfertilised \citep{cheesman1927, Niemenak2010}.

@@

\begin{figure}[h!]
	\centering
	\caption{\footnotesize {Phenology of cocoa in Colombia for crop modelling\\}} 
	\includegraphics[scale=0.3]{images/phenology.png}\\
	\footnotesize{Credits: Taken from from Dreamstime.com, phys.org \citep{toledo2021} and \cite{lopez2018}}
	\label{fig:pheno}
\end{figure}

\begin{figure}[h]
	\centering
	\caption{\footnotesize {Thermal time characterization of cocoa for four locations\\}}
	\includegraphics[scale=0.35]{images/yieldmonth.png}
	\label{fig:yield}
\end{figure}
\newpage

@@

\subsection{Climatological Conditions}
The temperature ranges from 16 to 28 $^\circ$C and it is relatively constant during the year. Saravena presented the maximum variability with hotter months during the first half of the year.  Apartado was found as the hottest with 26 $^\circ$C and Caldas as the coolest site with 18 $^\circ$C compared with other regions tested. Cali and Santander have similar temperature but contrasting PAR conditions. Santander and Caldas have the biggest variability and the maximum of solar radiation values over 20 MJ m$^{2}$day$^{-1}$. In contrast , Cali and Saravena presented the lowest values of PAR below 5 MJ m$^{2}$day$^{-1}$. (Fig.\ref{fig:temp})

Precipitation in Colombia is presented in two seasons per year from February to April and from October to November (Fig.\ref{fig:rain}). While the relative humidity

@@

@@

\begin{table}[h!]	
\caption {\footnotesize {Cocoa crop parameter values used in Species-parameterfile.}} \label{tab:Speparams} 
	\centering
	\begin{small}
		\begin{tabular}{{c c c c c c c c c }}
			\hline
			{\bf Tbase }& {\bf Topt } & {\bf RUE} & {\bf I50maxH}& {\bf I50maxW}& {\bf MaxT}& {\bf ExtremeT} & {\bf CO2-RUE}& {\bf S-water}\\
			\hline
			10& 26 & 0.8 & 100 & 5& 35&45&0.09&1.5 \\
			\hline
		\end{tabular}  
	\end{small}
\end{table}

\begin{table}[h!]	
\caption {\footnotesize {Cocoa crop parameter values used in Cultivar file.}}
\label{tab:Culparam} 
	\centering
	\begin{small}
		\begin{tabular}{c c c c c}
			\hline
			{\bf Cultivar }&{\bf Tsum }&{\bf HI}&{\bf I50A}&{\bf I50B}\\
			\hline
			ICS 95 & 3300 & 0.4 & 680 & 200 \\
			CCN51  & 3600 & 0.4 & 680 & 200 \\
			\hline
		\end{tabular}  
	\end{small}
\end{table}

\begin{table}[h!]	
	\caption {\footnotesize {Cocoa crop parameter values used in Treatment and Observation file.}} \label{tab:Treaparam} 
	\centering
	\begin{small}
		\begin{tabular}{{c c }}
			\hline
			{\bf Variable name }&{\bf Value}\\
			\hline
			Exp&KOKOlatl\\
			Label& Colombia\\
			Weather & KOKOS (.WTH file name)\\
			CO2 & 400\\
			SowingDate &flowering date\\
			SoilName & Loamy sand4\\
			Cultivar& ICS 95 or CCN51\\
			MaxIntercept& 0.95\\
			InitialBio & 1\\
			InitialTT & 0\\
			InitialFsolar & 0.01 \\
			LAI & 2 \\
			\hline
		\end{tabular}  
	\end{small}
\end{table}

@@

The SIMPLE model performance was evaluated by comparing simulated values cocoa yield with those reported by Fedecacao from cocoa plantations, using statistical indices of relative-RMSE (RRMSE) (Equ. \ref{equ:RMSE}) \citep{Zao2019simple} and coefficient of determination (R$^{2}$) (Equ. \ref{equ:R2}) \citep{Zao2019simple, Bai2020, Camargo2019aquacropr}. The harvest date predicted was supported by \textcolor{red}{Adriana results}
Yield reports from 20190 to 2020  were shared by Federación Nacional de Cacaoteros - Fedecacao.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\begin{figure}[h]
	\centering
	\caption{\footnotesize {Weather variables during flowering times}} 
	\includegraphics[scale=0.4]{images/averageS.png}\\
	\label{fig:weather}
\end{figure}

Studying the weather data effects over the flowering date and their final yield. We found that the number of successful flowers pollinated to produce final yield can be affected mostly by the rain, TMAX and wind (Figure \ref{fig:correlation}). The later can affect the availability of tiny flies pollinators from Diptera order and from the families of of the biting midges \textit{Ceratopogonidae},  genus  \textit{Forcipomyia} \citep{Saunders1959, kaufmann1975, sotomayor2020} to reach the cocoa flowers. However, wind is not included in the SIMPLE model as an input as cocoa crop has not been simulated with this model before. Flower opening is very well synchronised between the cohorts of mature flowers opening each night. The flowers open at almost exactly the same time and rate, irrespective of their position on the trunk. Unfertilised flowers abscise from the trunk approximately 1 day after flower opening  \citep{Niemenak2010}. 
\begin{figure}[h!]
	\centering
	\caption{\footnotesize {Pearson correlation among weather variables and flowering dates \\}} 
	\includegraphics[scale=0.7]{images/correlation.png}\\
	\label{fig:correlation}
\end{figure}.

\begin{figure}[h]
	\centering
	\caption{\footnotesize {Thermal time characterization of cocoa for four locations\\}} 
	\includegraphics[scale=0.5]{images/ttbbox.png}
	\label{fig:ttbox}
\end{figure}.
\newpage

\begin{figure}[h!]
	\centering
	\caption{\footnotesize {SIMPLE model output for cocoa in Colombia }} 
	\includegraphics[scale=0.3]{images/outmodel.png}\\
	\label{fig:m1}
\end{figure}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.
\textcolor{red}{this section on going to organize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

>>>>

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

@@

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------

@@

% Authors, for the paper (add full first names)
\Author{Angela Romero V $^{1,\dagger,\ddagger}$\orcidA{}, Adriana Gallego $^{1,\ddagger}$ and Anyela V. Camargo R.$^{1,}$*}

@@

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Romero, A.; Gallego, A.; Camargo, A.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Crop modelling can support agronomical decisions of crop production under a range of scenarios improving competitiveness. Cocoa production systems in Latin America has a high importance over social and economic development, facing  the fight against hunger and poverty. Cocoa fruits development can be considered as the result of a number of physiological and morphological processes that can be described by mathematical relationships even under uncontrolled environments. We parametrized the SIMPLE crop model \citep{Zao2019simple} to predict the best time for harvest cocoa fruits in Colombia. The aim of this study is develop a practical tool for farmers using flowering date and weather variables (Solar radiation, rain and temperature) easily available for crop modelling to understand and predict the phenology of cacao trees which is key to produce high quality cacao beans. \textcolor{blue}{need to complete}.  }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setcounter{section}{-1} %% Remove this when starting to work on the template.

@@

Cocoa is a cauliflorous plant, which means that flowers grow on the trunk and branches. In Colombia cocoa trees usually produce flowers throughout the year, however the biggest flowering occurs in September and January to harvest in March and July (Fig.\ref{fig:yield}). Cocoa trees produces with up to 10000 flowers per tree each year. which the 50 \%  do not develop into ripe fruits according to Fedecacao reports. The flower takes 30 days passing by 12 micro-stages from meristem development (stages 1–6) to the fully developed flower (Stages 7–12) \citep{swanson2005} when it is ready to be pollinated. 2005). The opening of flowers or anthesis  occurs over a 12-hour period during the night and it is synchronised between the groups of mature flowers \citep{Niemenak2010}. However, the live of a flower can last approximately 1 day after the opening falling form the trunk if it is unfertilised \citep{cheesman1927, Niemenak2010}.

@@

\begin{figure}[h!]
	\centering
	\caption{\footnotesize {Phenology of cocoa in Colombia for crop modelling.\\}} 
	\includegraphics[scale=0.3]{images/phenology.png}\\
	\footnotesize{Credits: Taken from from Dreamstime.com, phys.org \citep{toledo2021} and \cite{lopez2018}}
	\label{fig:pheno}
\end{figure}

\begin{figure}[h]
	\centering
	\caption{\footnotesize {Average of cocoa production characterization of cocoa for four locations\\}}
	\includegraphics[scale=0.35]{images/yieldmonth.png}\\
	{\footnotesize Flowering occurs in September and January to harvest six months latter in March and July respectively.}
	\label{fig:yield}
\end{figure}
\newpage

@@

\subsection{Climatological Conditions}
The temperature ranges from 16 to 28 $^\circ$C and it is relatively constant during the year. Saravena presented the maximum variability with hotter months during the first half of the year.  Apartado was found as the hottest with 26 $^\circ$C and Caldas as the coolest site with 18 $^\circ$C compared with other regions tested. Cali and Santander have similar temperature but contrasting PAR conditions. Santander and Caldas have the biggest variability and the maximum of solar radiation values over 20 MJ m$^{2}$day$^{-1}$. In contrast , Cali and Saravena presented the lowest values of PAR below 5 MJ m$^{2}$day$^{-1}$. (Fig.\ref{fig:temp}). Precipitation in Colombia is presented in two seasons per year from February to April and from October to November, hile the relative humidity remain constant (Fig.\ref{fig:rain}).

@@

\subsection{Thermal time for pod harvest date identification}
Thermal time (degree days) was calculated as cumulative sum of temperature from the flowering date to the pod harvest. It is required to model crop growth  considering the cocoa base temperature (T$_{b}$), at which the plant development stops \citep{Ritchie1991}. Thus a cocoa T$_{b}$ of 10$^\circ$C was considered according to \cite{lahive2019}. This characterization was conducted for the five regions counted 180 days (6 months) and 210 days (7 months just for Cladas) after flowering, as farmers used to harvest by calendar days. Characterizing the thermal time the models predicts the maturation day to harvest the cocoa can vary depending on temperature variations.

@@

\begin{table}[h!]	
\caption {\footnotesize {Cocoa crop parameter values used in Species-parameter file.}} \label{tab:Speparams} 
	\centering
	\begin{small}
		\begin{tabular}{{c c c c c c c c c }}
			\hline
			{\bf Tbase }& {\bf Topt } & {\bf RUE} & {\bf I50maxH}& {\bf I50maxW}& {\bf MaxT}& {\bf ExtremeT} & {\bf CO2-RUE}& {\bf S-water}\\
			\hline
			10& 26 & 0.6 & 100 & 5& 35&40&0.09&0 \\
			\hline
		\end{tabular}  
	{\footnotesize S-water is associated drought stress evaluations ranging from 0 (no water shortage) to 1 (extreme water shortage) \cite{Zao2019simple} }
	\end{small}
\end{table}

\begin{table}[h!]	
\caption {\footnotesize {Cocoa crop parameter values used in Cultivar file.}}
\label{tab:Culparam} 
	\centering
	\begin{small}
		\begin{tabular}{c c c c c}
			\hline
			{\bf Cultivar }&{\bf Tsum }&{\bf HI}&{\bf I50A}&{\bf I50B}\\
			\hline
			ICS 95 & 1912 & 0.3 & 680 & 200 \\
			CCN51  & 1912 & 0.3 & 680 & 200 \\
			\hline
		\end{tabular}  
	\end{small}
\end{table}

\begin{table}[h!]	
	\caption {\footnotesize {Cocoa crop parameter values used in Treatment and Observation file.}} \label{tab:Treaparam} 
	\centering
	\begin{small}
		\begin{tabular}{{c c }}
			\hline
			{\bf Variable name }&{\bf Value}\\
			\hline
			Exp&KOKOlatl\\
			Label& Colombia\\
			Weather & KOKOS (.WTH file name)\\
			CO2 & 400\\
			SowingDate &flowering date\\
			SoilName & Loamy sand4\\
			Cultivar& ICS 95 or CCN51\\
			MaxIntercept& 0.95\\
			InitialBio & 1\\
			InitialTT & 0\\
			InitialFsolar & 0.01 \\
			LAI & 1.8 \\
			\hline
		\end{tabular}  
	\end{small}
\end{table}

@@

The SIMPLE model performance was evaluated by comparing simulated values cocoa yield with those reported by Fedecacao from cocoa plantations, using statistical indices of relative-RMSE (RRMSE) (Equ. \ref{equ:RMSE}) \citep{Zao2019simple} and coefficient of determination (R$^{2}$) (Equ. \ref{equ:R2}) \citep{Zao2019simple, Bai2020, Camargo2019aquacropr}. The harvest date predicted was supported by \textcolor{red}{Adriana results}

Yield reports from 20190 to 2020  were shared by Federación Nacional de Cacaoteros Fedecacao.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

\subsection{Thermal time per region}
The thermal time characterization showed differences per region as was expected. Figure \ref{fig:ttbox} shows degree days ($^\circ$C) of cocoa growth cycles. Caldas had the lowest values and Apartado had the the highest results. this disttribucion is conincident with the temperature (Fig.\ref{fig:temp}). Meanwhile, Cali and Santander presented similar thermal time arround 2016 $^\circ$C.

\begin{figure}[h!]
	\centering
	\caption{\footnotesize {Thermal time characterization of cocoa for five locations.\\}} 
	\includegraphics[scale=0.3]{images/ttbbox.png}
	\label{fig:ttbox}
\end{figure}

\subsection{Weather effects}
Studying the weather data effects over the flowering date and their final yield. In a preliminary analysis of Santanter data, We found that the number of successful flowers pollinated to produce final yield can be affected mostly by the rain, TMAX and wind (Figure \ref{fig:correlation}). Farmers

\begin{figure}[h!]
	\centering
	\caption{\footnotesize {SIMPLE model output for cocoa in Colombia.\\ }} 
	\includegraphics[scale=0.35]{images/outmodel.png}
	\label{fig:m1}
\end{figure}

\subsection{Day of harvest prediction}
\begin{figure}[h!]
	\centering
	\caption{\footnotesize {Day of harvest cocoa simulation\\ }} 
	\includegraphics[scale=0.4]{images/RegionHarvest.png}
	\label{fig:dayH}
\end{figure}
%\begin{figure}[h!]
%	\centering
%	\caption{\footnotesize {Weather variables during flowering times.\\}} 
%	\includegraphics[scale=0.4]{images/averageS.png}
%	\label{fig:weather}
%\end{figure}

\begin{figure}[h!]
	\centering
	\caption{\footnotesize {Pearson correlation among weather variables and flowering dates all locations. \\}} 
	\includegraphics[scale=0.5]{images/heatm.png}\\
	\label{fig:heat}
	{\footnotesize thermalT= thermal time without Tb. ttb= thermal time with Tb. WS2M= Wind Speed at 2 Meters (m/s). T2MDEW = Dew/Frost Point at 2 Meters ($^\circ$C) }
\end{figure}
\newpage

\section{Discussion}
Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

The optimum temperature for photosynthesis in cacao has
been reported to be between 31 °C and 33 °C (Balasimha et al.
1991) and 33 °C–35 °C (Yapp 1992). Sena Gomes and
Kozlowski (1987) reported a decrease in gs over the range
18.7 °C to 27.2 °C and an increase at temperatures above this,
most likely to enhance cooling at higher temperatures.
However, the opposite effect was described by Raja Harun
and Hardwick (1988a). In this study, gs and transpiration (E)
increased within the range of 20 °C–30 °C. In field-grown
cacao in India, photosynthetic rate declined as mean monthly
temperature increased above 34 °C during the dry season
(Balasimha et al. 1991). \cite{lahive2019}
\textcolor{red}{this section on going to organize}

@@

\subsection{Weather Effects}
Wind can affect the availability of tiny flies pollinators from Diptera order and from the families of of the biting midges \textit{Ceratopogonidae},  genus  \textit{Forcipomyia} \citep{Saunders1959, kaufmann1975, sotomayor2020} to reach the cocoa flowers. However, wind is not included in the SIMPLE model as an input as cocoa crop has not been simulated with this model before. Flower opening is very well synchronised between the cohorts of mature flowers opening each night. The flowers open at almost exactly the same time and rate, irrespective of their position on the trunk. Unfertilised flowers abscise from the trunk approximately 1 day after flower opening  \citep{Niemenak2010}. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
